Supplementary Materials- A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-06-11 analysis/paper/supplementary-material.Rmd
correct the caption of bgof figures

```{r figure-bgof-pre-E, fig.cap = "Goodness-of-fit diagnostics for the pre-European model (top) and the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/003-pre-bgof.png"))
```

```{r figure-bgof-post-E, fig.cap = "Goodness-of-fit diagnostics for the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/004-post-bgof.png"))
```

>>>>

```{r figure-bgof-pre-E, fig.cap = "Goodness-of-fit diagnostics for the pre-European model and the post-European model (below). Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/003-pre-bgof.png"))
```

```{r figure-bgof-post-E, fig.cap = "Goodness-of-fit diagnostics for the post-European model. Boxplots represent distributions calculated on 100 network graphs simulated from the estimated posterior distribution. Red lines represent distributions of observed networks, and black lines show the 95% intervals."}
knitr::include_graphics(here::here("analysis/figures/004-post-bgof.png"))
```
